---
title: "Data Import Practice"
format: 
  html:
    self-contained: true
editor: visual
---

## Setup

```{r}
#| warning: false
#| message: false

library(tidyverse)

```

## Step 1: Read in the dataset `ages.csv`.

Question 1.

```{r}
# Code to read in the ages.csv data goes here! 

ages_csv <- read_csv(here::here("supporting_artifacts", "learning_targets",
                                "datasets", "Ages_Data", "ages.csv"))

```

## Step 2: Read in the dataset `ages_tab.txt`

Question 2.

```{r}
# Code to read in the ages_tab.txt data goes here! 

ages_tab <- read_tsv(here::here("supporting_artifacts", "learning_targets",
                                "datasets", "Ages_Data", "ages_tab.txt"))


```

## Step 3: Read in the dataset `ages_mystery.txt`

Question 3.

```{r}
# Code to read in the ages_mystery.txt data goes here! 

ages_mystery <- read_delim(here::here("supporting_artifacts", "learning_targets", 
                                      "datasets", "Ages_Data", "ages_mystery.txt"),
                           delim = "|")


```

## Step 4: Read in the dataset `ages.xlsx`

Question 4.

```{r}
# Code to read in the ages.xlsx data goes here! 

ages_excel <- read_excel(here::here("supporting_artifacts", "learning_targets", 
                                    "datasets", "Ages_Data", "ages.xlsx"))

```

## Step 5: Both `read.csv` and `read.table` have an optional argument called `stringsAsFactors`. Figure out what this does.

## Step 6: Find a way to use `read_csv()` to read `ages.csv` with the variable "Name" as a factor and "Age" as a character.

Question 5.

```{r}
# Code to read in the ages.csv with "Name" as a factor and "Age" as a character goes here! 

ages_factors <- read_csv(here::here("supporting_artifacts", "learning_targets", 
                                    "datasets", "Ages_Data", "ages.csv"), 
                         col_types = cols( Name = col_factor(),
                                           Age = col_character()
                                           ))


```

------------------------------------------------------------------------
