---
title: "Lab 9 Rowe"
author: "Joshua Rowe"
format: 
  html:
    code-fold: true
    self-contained: true
editor: visual
---

## Setup

```{r}
#| warning: false
#| message: false

library(tidyverse)

StateNames_A <- read_csv(here::here("supporting_artifacts", "learning_targets", 
                                    "datasets", "StateNames_A.csv"))

```

## Part 1

Question 1.

```{r 1-1}
#| warning: false
#| message: false

Allison <- StateNames_A |> 
  filter(Name == "Allison") |> 
  mutate(Gender = str_replace_all(Gender, c("F" = "F_at_Birth", 
                                            "M" = "M_at_Birth"))) |> 
  group_by(State, Gender) |> 
  summarize(Count = sum(Count)) |> 
  pivot_wider(names_from = Gender, values_from = Count, values_fill = 0)

```

Question 2.

```{r 1-2}

Allison <- Allison |> 
  select(State, F_at_Birth)

```

Question 3.

```{r 1-3}

StateNames_Allison <- StateNames_A |> 
  filter(Name == "Allison") |> 
  group_by(Year) |> 
  summarize(Count = sum(Count)) |> 
  mutate(Year_fact = as.factor(Year))

ggplot(data = StateNames_Allison) + 
  geom_col(mapping = aes(x = Year_fact, y = Count), fill = "navy") + 
  labs(x = "Year", y = "", subtitle = "Number of babies named \'Allison\'") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) + 
  theme(plot.title.position = "plot")

```

## Part 2

Question 4.

```{r 2-1}

Linear_Model <- StateNames_Allison |> 
  lm(Count ~ Year, data = _)

```

Question 5.

```{r 2-2}
#| warning: false
#| message: false

ggplot(data = StateNames_Allison, mapping = aes(x = Year, y = Count)) + 
  geom_point(color = "darkblue") + 
  geom_smooth(method = lm, se = FALSE, color = "tomato")

```

Question 6.

```{r 2-3}

print(str_c("Count = ", Linear_Model$coefficients[2], "*Year + ", Linear_Model$coefficients[1]))

```

Question 7.

```{r 2-4}

StateNames_Allison <- StateNames_Allison |> 
  mutate(Residuals = Linear_Model$residuals)

ggplot(data = StateNames_Allison, mapping = aes(x = Year, y = Residuals)) + 
  geom_point()

```

I do not see any pattern in the residuals, which is good! The two relatively large residuals catch my attention, but they are not so large that they would make me assume the model is incorrect.

4.  What do you conclude from this model? Is my name not cool anymore?

While the model does point out a negative trend, I'm not sure that I would conclude that the name is "not cool" anymore! The name "Achilles," I think, is very cool but the website <https://www.everything-birthday.com/name/m/Achilles> suggests, it has had many periods where its popularity "decreased" over time!

## Part 3

Question 8.

```{r 3-1}


Allan <- StateNames_A |> 
  filter(Name == "Allan" | Name == "Alan" | Name == "Allen", 
         Gender == "M") |> 
  mutate(Sex = str_replace_all(Gender, c("M" = "M_at_Birth"))) |> 
  select(Name, Year, State, Count, Sex)



```

Question 9.

```{r 3-2}

CA_PA <- Allan |> 
  pivot_wider(names_from = Name, values_from = Count, values_fill = 0) |> 
  filter(State == "CA"| State == "PA", Year == 2000)

```

Question 10.

```{r 3-3}

num_to_Percent <- function(df, vars) {
  
  Total <- rowSums(df[vars])
  
  df <- df[vars] / Total * 100
}

CA_PA$percent <- num_to_Percent(df = CA_PA, vars = c("Allen", "Alan", "Allan"))


```
