---
title: "Week 9 Practice Activities"
author: "Josh Rowe"
format: 
  html: 
    self-contained: true
editor: visual
---

## Setup

```{r}
#| warning: false
#| message: false

library(tidyverse)

mystery_animal <- read_csv(here::here("supporting_artifacts", "learning_targets", 
                                    "datasets", "mystery_animal.csv"))


```

## Linear Model

Fit a linear regression to determine if the Duck Diet is associated with the animal gaining weight, losing weight, or neither.

Plot the residuals (observed value minus predicted value) of your linear model versus `weight_before`.

Question 1.

```{r}

linear_model <- mystery_animal |> 
  lm(weight_after ~ weight_before, data = _)

model_info <- broom::augment(linear_model)

ggplot(data = model_info, mapping = aes(x = weight_before, y = .resid)) + 
  geom_point()

# This is so cool!!

```

## Simulation

You manage to intercept a shipping notice for delivery to Professor Hill. It says the following:

    Wells Fargo Shipment 1957

    To:  Harold Hill, Mason City, Iowa
    From:  Music Factory, Gary, Indiana

    Items included:
        Trombones: 76
        Cornets: 110
        Saxophones: 542
        Clarinets: 318
        Bassoons: 175
        
    Total Shipped Weight: 4532 lbs.

This is your chance to catch Professor Hill in his lie!

First, write a function that samples the correct number of weights of trombones, cornets (trumpets), and reed instruments (saxophones, clarinets, bassoons), and then returns the total weight of the shipment.

Then, use that function to create random samples of the total weight of 1000 possible shipments.

(Some code is provided for you below. Do not change the seed!)

Question 2.

```{r}

trumpet_95 <- qunif(p = 0.95, min = 1.5, max = 3.5)

trombone_10 <- qnorm(p = 0.10, mean = 4.6, sd = 0.8)

trombone_5lb <- 1 - pnorm(q = 5, 
                          mean = 4.6, 
                          sd = 0.8)

trombone <- rnorm(n = 100, mean = 4.6, sd = 0.8)

trombone_4lb_sim <- length(trombone[trombone < 4])


music_man <- function(n_tromb, n_cor, n_reed){
  
  trombones <- rnorm(n_tromb, mean = 4.6, sd = 0.8)
  cornets <- runif(n_cor, min = 1.5, max = 3.5)
  reeds <- rchisq(n_reed, df = 4)
  
  return(sum(trombones, cornets, reeds))
  
}

set.seed(1957)

my_weights <- rerun(.n = 1000, 
                    music_man(n_tromb = 76, n_cor = 110, n_reed = 1035)
                    ) |> 
  flatten_dbl()

weights_under_4532lb <- length(my_weights[my_weights < 4532])

```
